\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{subcaption}
\usepackage{float}
\usepackage{dblfloatfix}
\usepackage{placeins}
\usepackage[hidelinks]{hyperref}




\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Time-optimal Flying a VTOL Drone}

\author{\IEEEauthorblockN{Larissa Rickler}
\IEEEauthorblockA{(03697651)\\
larissa.rickler@tum.de}
\and
\IEEEauthorblockN{Leonardo Igler}
\IEEEauthorblockA{(03702035)\\
leonardo.igler@tum.de}






}

\maketitle




\begin{abstract}

This milestone report describes our group's first experiments in training a drone to follow simple 2D trajectories using deep reinforcement learning methods.

\end{abstract}

%\begin{IEEEkeywords}
%reinforcement learning, VTOL drone, neural network controller
%\end{IEEEkeywords}

\section{Methods}
\label{sec:methods}
\input{sections/methods}

\section{Experiments}
\label{sec:experiments}
\input{sections/experiments}

\section{Results}
\input{sections/results}

\section{Future Work}
\input{sections/future_work}






\bibliographystyle{IEEEtran}
\bibliography{milestone-report}

\end{document}



\iffalse
Lecture Website:
Milestone Report and Presentation
Your milestone report should be one page and answer the following questions:
1. What experiments have you conducted so far?
2. Are there any changes to the research hypothesis or problem statement from the proposal?

The milestone report must report on at least one experiment that you have done since the proposal. This experiment does not need to be successful, but you should have attempted something. If it did not work as expected, you should briefly discuss why. You are encouraged to include a plot or figure.


Piazza:
Your milestone report should be 1 - 2 (max) pages and answer the following questions:
1. What has been done so far? (tools decided on, implementations, overview on methods, …)
2. First Results (e.g., some raw plots)
(no explicit introduction, because you described your topic already in the proposal)

The milestone report must report on at least one experiment that you have done since the proposal. This experiment does not need to be successful, but you should have attempted something. If it did not work as expected, you should briefly discuss why. You are encouraged to include a plot or figure.

TODO:
\fi